### 2021-08-18 mycv/subs/papers.tex
update

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
  % ---------------------------------------------------------
  \cventry
  {\underline{Y. Jeong}$^*$, C N. Tom\'{e}, B. Jeon}
  {Finite element analysis of incremental elasto-visco-plastic self-consistent polycrystal model}
  {}
  {in preparation}
  {
  }
  % ---------------------------------------------------------
  \cventry
  {\underline{Y. Jeong}$^*$, C. N. Tom\'{e}}
  {\href{https://doi.org/10.1016/j.ijplas.2020.102812}{An efficient elasto-visco-plastic self-consistent formulation: Application to steel subjected to loading path changes}}
  {International Journal of Plasticity}
  {Vol. 135, 102812, 2020}
  {
  }
  % ---------------------------------------------------------
  \cventry
  {\underline{Y. Jeong}$^*$, D. Steglich}
  {\href{https://doi.org/10.1016/j.ijmecsci.2020.105680}{Modelling-assisted description of anisotropic edge failure in magnesium sheet alloy under mixed-mode loading}}
  {International Journal of Mechanical Sciences}
  {Vol. 181, 105680, 2020}
  {
  }

>>>>

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
  % ---------------------------------------------------------
  \cventry
  {\underline{Y. Jeong}$^*$, B. Jeon, C N. Tom\'{e}}
  {Finite element analysis using an incremental elasto-visco-plastic self-consistent polycrystal model: FE simulations on Zr and low-carbon steel subjected to bending, stress-relaxation, and unloading}
  {submitted to International Journal of Plasticity}
  {Under review}
  {
  }
  % ---------------------------------------------------------
  \cventry
  {\underline{Y. Jeong}$^*$, C. N. Tom\'{e}}
  {\href{https://doi.org/10.1016/j.ijplas.2020.102812}{An efficient elasto-visco-plastic self-consistent formulation: Application to steel subjected to loading path changes}}
  {International Journal of Plasticity}
  {Vol. 135, 102812, 2020}
  {
  }
  % ---------------------------------------------------------
  \cventry
  {\underline{Y. Jeong}$^*$, D. Steglich}
  {\href{https://doi.org/10.1016/j.ijmecsci.2020.105680}{Modelling-assisted description of anisotropic edge failure in magnesium sheet alloy under mixed-mode loading}}
  {International Journal of Mechanical Sciences}
  {Vol. 181, 105680, 2020}
  {
  }
